Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2021-12-27 paper.tex
Clarify aims in discussion

>>>>

\rev{Our aim in performing the reported numerical experiments was to explore
the flute instability in a dynamically twisted coronal flux tube, specifically
focussing on the effect of anisotropic viscosity on the development of the
instability. In addition we wish to understand the effect the instability has
on the proceeding kink instability, the effect on the overall heating generated
through viscous and Ohmic dissipation, and the effect that varying resistivity
has on the development of the flute.}
